Design of Blur Invariant Fiducial for Low Cost Quadcopter

### 2014-02-28 ECCV/paper.tex
Added Introduction about quadcopter navigation. Added missing figure.

\section{Introduction}
A fiducial marker or simply a fiducial is an synthetic object placed in the
scene, which can provide additional information about the environment. Sometimes
naturally available features in a scene may be used as replacement to fiducials.
But, natural features may not be available always and quality cannot be
guranteed in every scene. So, results are not satisfactory in uncontrolled
environment and hence use of such features is limited. Artificial fiducials are
widely used in Augmented Reality(AR)\cite{Zhang:2002}\cite{Dorfmuller99}
applications, vision based navigation of robots\cite{Davison:2007} etc.

Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
in various tracking activities (e.g. aerial surveillance, search and rescue
operations etc.).Low cost quadcopters such as AR Drone are very unstable which
causes non-uniform motion resulting lot of motion blur in captured images.
Also, as image transfer is done through wireless media using User Datagram
Protocol (UDP), there is possibility of missing intermediate frames . It
results in lower frame rate (around 15 frames per second (FPS)) instead of
normal rate of 30 FPS. This frequent dropping of frames may cause drastic
change in position of object in successive frames. Thus, performance of
traditional tracking methods is not satisfactory for tracking through
quadcopters. Our aim is to design a fiducial which we will be able to track
under significant amount of motion blur and is robust in terms of drastic
change in its position in successive frames.

@@

From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
ARTag drastically with increase in blur scale.

We have also analysed the recognition rate along different blur orientations at
different blur scales. We found that per blur scale, at certain blur
orientations, recognition of ARTag fails. Table shows the range of blur angles
for which we are able to recognise the ARTag at different blur scales.

\begin{table}
\caption{Blur angle range}
\centering
\begin{tabularx}{0.75\textwidth}{|Y|Y|}
\cline{1-2}
Blur Scale & Blur Angle Range \\ \cline{1-2}
35 & 32--58 \\ \cline{1-2}
40 & 41--48 \\ \cline{1-2}
45 & 41--48 \\ \cline{1-2}
50 & 44--46 \\ \cline{1-2}
\end{tabularx}
\end{table}

>>>>

\section{Introduction}
Recently, use of Unmanned Aerial Vehicles(UAV) such as quadcopters is increased
in various tracking activities e.g. aerial surveillance, search and rescue
operations etc. Navigation of these vehicles is mainly based on the
onboard inertial sensors. But sensor based measurments are prone to errors. So,
visual cues captured through onboard camera can be used along with the sensor
based measurments.  But, natural features may not be available always and
quality cannot be guranteed in every scene. So, results are not satisfactory in
uncontrolled environment and hence use of such features is limited specifically
when we need very high precision.

Artificial markers are used when we need high precision. A fiducial marker or
simply a fiducial is an synthetic object placed in the scene, which can provide
additional information about the environment. Artificial fiducials are widely 
used in Augmented Reality(AR) \cite{Zhang:2002}\cite{Dorfmuller99}
applications, vision based navigation of robots\cite{Davison:2007} etc.

Low cost quadcopters such as AR Drone are very unstable which
causes non-uniform motion resulting lot of motion blur in captured images.
Also, as image transfer is done through wireless media using User Datagram
Protocol (UDP), there is possibility of missing intermediate frames . It
results in lower frame rate (around 15 frames per second (FPS)) instead of
normal rate of 30 FPS. This frequent dropping of frames may cause drastic
change in position of object in successive frames. Thus, performance of
traditional tracking methods is not satisfactory for tracking through
quadcopters. Our aim is to design a fiducial which we will be able to track
under significant amount of motion blur and is robust in terms of drastic
change in its position in successive frames.

@@

From Table \ref{tab:ARTag_blur}, it can be clearly seen that performance of
ARTag drastically degrade with increase in blur scale.

We have also analysed the recognition rate along different blur orientations
(from 0 to 90 degrees) at different blur scales. We found that per blur scale,
at certain blur orientations, recognition of ARTag fails. Table shows the range
of blur angles for which we are able to recognise the ARTag at different blur
scales. From Table \ref{tab:artag_blurangle}, it can be seen that, when blur
scale is greater than 30, ARTag is not recognisable with horizontal blur
orientation(blur angle near zero degrees) as well as vertial blur
orientation(blur angle near 90 degrees).

\begin{table}
\caption{Blur angle range}
\centering
\begin{tabularx}{0.75\textwidth}{|Y|Y|}
\cline{1-2}
Blur Scale & Blur Angle Range \\ \cline{1-2}
30 & 0 -- 90\\ \cline{1-2}
35 & 32 -- 58 \\ \cline{1-2}
40 & 41 -- 48 \\ \cline{1-2}
45 & 41 -- 48 \\ \cline{1-2}
50 & 44 -- 46 \\ \cline{1-2}
\end{tabularx}
\label{tab:artag_blurangle}
\end{table}
